Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-10 WRITEUP/ms.tex
if condition for style (not compiling for me otherwise)

% --------------------------------------------
% \documentclass[twocolumn]{aastex6}
% \documentclass[apj]{emulateapj}
%\documentclass[iop]{emulateapj_old} 
\documentclass[iop]{emulateapj} 
\usepackage{amsmath}

\input{preamble}
\slugcomment{Paper draft for the project developed at the Kavli Summer Program in Astrophysics 2018. 
To be Submitted.}

@@

\def\figpath{./Fig}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/}
\caption{
SFR and gas surface densities of MCs identified in \flower in \ncode{serra} (star symbols) compared to those 
observed in 0\,$\lesssim$\,\z$\lesssim$\,2 galaxies.
Literature data are compiled from \citealt{Kennicutt98a, Bouche07a, Daddi10a, Daddi10b, Genzel10a, Tacconi10a} and 
\citealt{Pallottini17b}.
%The literature data are compiled from \citealt{Leroy13a, Genzel13a, Sharon13a, Hodge15a}, \citealt{Pallottini17b} 
%and references therein, and Sharon et al. in prep.
\label{fig:sk}}
\end{figure*}

>>>>

% --------------------------------------------

% AP: I have some compatibility issues with the new style (i.e. \section does not work)
\IfFileExists{emulateapjlegacy.cls}{\documentclass[iop]{emulateapjlegacy}}{\documentclass[iop]{emulateapj}}

\usepackage{amsmath}
\input{preamble}
\slugcomment{Paper draft for the project developed at the Kavli Summer Program in Astrophysics 2018. 
To be Submitted.}

@@

% it can be instead included as
% \graphicspath{{Fig/}}
% so that plots are automatically searched for in the given path
\def\figpath{./Fig}

@@

\begin{figure*}[htbp]
\centering
%\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/CMF_.png}
\caption{
\AP{figure not found in the path}
SFR and gas surface densities of MCs identified in \flower in \ncode{serra} (star symbols) compared to those 
observed in 0\,$\lesssim$\,\z$\lesssim$\,2 galaxies.
Literature data are compiled from \citealt{Kennicutt98a, Bouche07a, Daddi10a, Daddi10b, Genzel10a, Tacconi10a} and 
\citealt{Pallottini17b}.
%The literature data are compiled from \citealt{Leroy13a, Genzel13a, Sharon13a, Hodge15a}, \citealt{Pallottini17b} 
%and references therein, and Sharon et al. in prep.
\label{fig:sk}}
\end{figure*}
